Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-10-17 Presentacion.tex
Changes of Plants

\documentclass[10pt,a4paper]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{verbatim}
\usefonttheme{professionalfonts} % fuentes de LaTeX
\usetheme{Szeged}
\usecolortheme{beaver}
\setbeamercovered{transparent}

\begin{document}
%\font\myfont=cmr12 at 20pt
%\title{{\myfont Precise Weed and Maize Classification through Convolutional Neuronal Networks}}
%\author{{\bf C\'ordova Andrea\inst{1}, Barreno Mauricio, J\'acome Jos\'e }\\
%\institute{
%\inst{1}%
 % Universidad de las Fuerzas Armadas ESPE\\
 % Latacunga - Ecuador}
%{ 2nd IEEE Ecuador Technical Chapters Meeting}
%\vspace*{1cm}}
%\date{October 2017}
\title[Precise Weed and Maize Classification through Convolutional Neuronal Networks] %optional
{Precise Weed and Maize Classification through
Convolutional Neuronal Networks}

@@

\date[Ecuador] % (optional)
{2nd IEEE Ecuador Technical Chapters Meeting, October 2017}
\logo{\includegraphics[height=1.5cm]{espe.png}}
\frame{\titlepage}
\frametitle{Presentation Outline}
\tableofcontents
%\newpage
\section{Introduction}
\frametitle{Introduction}
\textbf{Introduction}
\item Maize is one of the most important crops of the world.
\item Weed can affect maize crop yield up to 5000 Kg/Ha.\footnote{suarez2005distintos} %Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
\item Robotics has had significant contributions to Precision Agriculture.%La robotica esta presentando grandes avances en la agricultura de precision.
\item Artificial Intelligence reached near-to-human precision.%Inteligencia artificial cada vez se acerca mas a la inteligencia humana.
\textbf{Purpose of the present study}
\item Obtain samples to conform a dataset%Obtener muestras(imagenes) para conformar un dataset.
\item Segment samples%Segmentar las muestras.
\item Test different network architectures of Convolutional Neural Networks for Maize and Weed Clasification %Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
\item Benchmark the best network architecture to analyze processing time %Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
\item Optimize the network processing speed %Optimizar la red.
\section{Used Hardware and Software}
\frametitle{Used Hardware and Software}
\textbf{Hardware}
\item Raspberry Pi 3.
\item Pi camera V2.1.
\item Nvidia graphic Card GTX950M.
\textbf{Software}
\item OpenCV Library
\item Caffe framework
\item Ubuntu 16.04
\item PIXEL Distribution derived from Debian.
\section{Image Processing}
	\item Acquire  an RGB image through RPi Camera v2.1
	\item Detect contours and crop image to the contour
	\item Normalize Green Channel and then $S = 2*G - R - B$ \footnote{wang2013path}
	\item OTSU Thresholding
	\item Mask image

@@

	\includegraphics[width=3.5 in]{procesamiento}
	\caption{The process of image processing,\textbf{ por lo pronto}}

@@

@@

\item Rotated images every 30º to improve plant detection \footnote{sladojevic2016deep}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.

@@

@@

	\item Weed Plants \textit{(Zea maiz)}

@@

	\item Tested on classification of plants, \footnote{cheng2015feature} \footnote{potena2016fast} \footnote{di2016automatic}

@@

	\item cNET and sNET \footnote{potena2016fast}

@@

%-----------------------------
%\bibliographystyle{plain}
\bibliography{bibliografiapaper}
\end{document}

>>>>

\documentclass[10pt,a4paper]{beamer}
\usepackage[backend=biber]{biblatex}
\addbibresource{bibliografiapaper}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{verbatim}
\usefonttheme{professionalfonts} % fuentes de LaTeX
\usetheme{Szeged}
\usecolortheme{beaver}
\setbeamercovered{transparent}

\begin{document}
\title[Precise Weed and Maize Classification through Convolutional Neuronal Networks] %optional
{Precise Weed and Maize Classification through
Convolutional Neuronal Networks}

@@

\date[Ecuador] % (optional)
{2nd IEEE Ecuador Technical Chapters Meeting, October 2017}
\logo{\includegraphics[height=1.5cm]{espe.png}}
\frame{\titlepage}
%-----------------------------
\begin{frame}
\frametitle{Presentation Outline}
\tableofcontents
%\newpage
\end{frame}
%-----------------------------
\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}
\section{Introduction}
\begin{frame}
\frametitle{Introduction}
\textbf{Introduction}
\begin{itemize}
\item Maize(\textit{Zea mays}) is one of the most important crops of the world.
\item Weed can affect maize crop yield up to 5000 Kg/Ha.\footnote{ R. SU\'AREZ and J. P. Y. J. VALLADARES, “Distintos sistemas de escarda en ma\'iz forrajero,” \textit{Producciones agroganaderas: Gesti\'on eficiente
y conservaci\'on del Medio Natural. Actas de la XLV RC de la SEEP. Gij\'on}, 2005.} %Las malas hierbas en el maiz pueden afectan hasta 5000 Kg/Hectaria de produccion.
\item Robotics has had significant contributions to Precision Agriculture.%La robotica esta presentando grandes avances en la agricultura de precision.
\item Artificial Intelligence reached near-to-human precision.%Inteligencia artificial cada vez se acerca mas a la inteligencia humana.
\end{itemize}
\textbf{Purpose of the present study}
\begin{itemize}
\item Obtain samples to conform a dataset%Obtener muestras(imagenes) para conformar un dataset.
\item Segment samples%Segmentar las muestras.
\item Test accuracy in different network architectures of Convolutional Neural Networks for Maize and Weed Clasification %Probar diferentes arquitecturas de Redes Neuronales Convolucionales para entrenar la red.
\item Benchmark the best network architecture to analyze processing time %Hacer Benchmark en diferentes hardwares para analizar tiempos de procesamiento.
\item Optimize the network processing speed %Optimizar la red.
\end{itemize}
\end{frame}
%-----------------------------
\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}
\section{Used Hardware and Software}
\begin{frame}
\frametitle{Used Hardware and Software}
\textbf{Hardware}
\begin{enumerate}
\item Raspberry Pi 3.
\item Pi camera V2.1.
\item Nvidia graphic Card GTX950M.
\end{enumerate}
\textbf{Software}
\begin{enumerate}
\item OpenCV Library
\item Caffe framework
\item Ubuntu 16.04
\item PIXEL Distribution derived from Debian.
\end{enumerate}
\begin{figure}[hbtp]
%\caption{•}
\centering
\includegraphics[scale=0.3]{SoftHard.png}
\end{figure}

\end{frame}
%-----------------------------
\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}
\section{Image Processing}
\begin{frame}
\begin{itemize}
	\item Acquire  an RGB image through RPi Camera v2.1(Centered to the plant)

	\item Normalize Green Channel and then $S = 2*G - R - B$ \footnote{ P. Wang, Z. Meng, C. Luo, and H. Mei, “Path recognition for agricultural robot vision navigation under weed environment,” in \textit{7th International Conference on Computer and Computing Technologies in Agriculture (CCTA)}, no. Part I. Springer, 2013, pp. 242–248.
}
	\item OTSU Thresholding
	\item Detect contours and crop image to the contour 
	\item Mask image

@@

	\includegraphics[width=3.5 in]{SegmentationPaper}
	\caption{Steps of image processing(Cropped image)}

@@

    \frametitle{Table of
     Contents}

@@

\item Rotated images every 30º to improve plant detection \footnote{ S. Sladojevic, M. Arsenovic, A. Anderla, D. Culibrk, and D. Stefanovic, “Deep neural networks based recognition of plant diseases by leaf image classification,” \textit{Computational intelligence and neuroscience}, vol. 2016, 2016.
}%Imagenes rotadas cada 30 grados para mejorar la deteccion de las planta.

@@

	%\caption{Normal architecture in a Convolutional Neural Network}

@@

	\item Weed Plants \textit{(Urtica Urens, Lysimachia vulgaris , Chenopodium \'album , Malva Capestri)} \footnote{COBA ROBALINO, José María. \textit{Monografía General del Cantón Píllaro.}} %Ortiga, Allpaquinua Cuchimalva, Forastera, Allpaquinua,  

@@

	\item Tested on classification of plants, \footnote{B. Cheng and E. T. Matson, “A feature-based machine learning agent for automatic rice and weed discrimination.”} \footnote{ C. Potena, D. Nardi, and A. Pretto, “Fast and accurate crop and weed identification with summarized train sets for precision agriculture”

@@

	\item cNET and sNET \footnote{ C. Potena, D. Nardi, and A. Pretto, “Fast and accurate crop and weed identification with summarized train sets for precision agriculture”

@@

%-----------------------------
%\bibliographystyle{plain}
%\bibliography{bibliografiapaper}
\end{document}
